### 2013-07-24 4/polsar.tex
updated for Ian changes

\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
\label{chap:polsar}

In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
Then log-transformation is shown converting these into an additive and homoskedastic model.
Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
Finally the last section strengthens our model showing the matching between simulation and real-life captured data
  not only for a few dimensionally-collapsed single-dimensional measures
  but also for all elements of the multi-dimensional POLSAR covariance matrix.

@@

In this section, the POLSAR scattering vector is denoted as $s$.
In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
  the vector is two-dimensional ($d=2$) and is normally written as: 
\begin{equation}
s_{part}=\begin{bmatrix}
S_h\\ 
S_v
\end{bmatrix}
\end{equation}
In the case of full and monostatic POLSAR data,
  the vector is three-dimensional ($d=3$) and is presented as:
\begin{equation}
s_{full}=\begin{bmatrix}
S_{hh}\\
\sqrt{2}S_{hv}\\
S_{vv}
\end{bmatrix}
\end{equation}

Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
Assuming all the elements in $s$ are independent
  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
  then the probably density function (PDF) of $s$ can be written as:
\begin{equation}
  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
\end{equation}
where $|M|$ denotes the determinant of the matrix $M$.

As covariance matrix is only defined on multiple data points,
  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
They are formed as the mean of Hermitian outer product of single-look scattering vectors
\begin{equation}
  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
\end{equation}
with $s_i$ denotes the single-look scattering vector,
  which equals $s_{part}$ in the case of partial POLSAR and
  $s_{full}$ in the case of full polarimetry,
and $L$ is the number of looks.

Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
$Z=LC_v$, whose PDF is given as:
\begin{equation}
  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
\end{equation}
with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
and $d$ is the dimensional number of the POLSAR covariance matrix.

Our approach differs by applying the homoskedastic log transformation
  on a less-than-well-known result for the deterimant of the covarinace matrix.
  %under the assumption of circular complex Gaussian distribution
  %applicable for POLSAR data.
In \cite{Goodman_1963_AMS_178}, %Goodman
it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
\begin{equation}
\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
\label{eqn:prod_chi_squared_rv}  
\end{equation}

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\label{eqn:sum_log_chi_squared_rv}
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
\label{sec:polsar_heterosked_model_and_log_transform}

In this section the multiplicative nature of POLSAR data is illustrated.
Log-transformation is shown converting this into a more familiar additive model.
Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
  is proved to be the case for the original POLSAR data.
In log-transformed domain, the case for a homoskedastic model,
  where  variance is fixed and be independent of the underlying mean,
  is demonstrated.
To keep the section flowing, the mathematical derivation is only presented here in major sketches.
For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.

From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
we have:
\begin{eqnarray}
  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
\label{eqn:log_determinant_distribution}  
\end{eqnarray}

In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
  the logarithmic transformation converts this into a more familiar additive noise.

Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
\begin{equation}
pdf(x;k) =
  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
\label{eqn:chi_squared_dist_pdf:chap4}
\end{equation}
Applying the variable change theorem, 
  its log-transformed variable follows the PDF of:
\begin{equation}
  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
\end{equation}

Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
  can be written as:
  \begin{eqnarray}
    CF_\chi(t) &=& (1-2it)^{−L} \\ 
    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
  \end{eqnarray}
Subsequently their means and variances can be computed from the given characteristic functions as:
  \begin{eqnarray}
    avg \left[ \chi(2L) \right]&=&2L \\
var \left[ \chi(2L) \right]&=&4L \\
avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
var \left[ \Lambda(2L) \right] &=& \psi^1(L)
  \end{eqnarray}
  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma function respectively.

@@

Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
\begin{eqnarray}
  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
\end{eqnarray}

Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
  the underlying $\Sigma_v$ is expected to differ from one region to the next.
Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
  %and it is clear that 
  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.

@@

Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
  this section introduces the consistent sense of distance in a few different perspective.
First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
the following random variables,
  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observable according to their definitions:
%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :

\begin{eqnarray}
  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
\begin{eqnarray}
  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
\end{eqnarray}

Taking the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
\begin{eqnarray}
\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
\label{eqn:log_determinant_distance_distribution} \\ 
 \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
\label{eqn:dispersion_distribution} \\ 
 \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
\label{eqn:contrast_distribution}  
\end{eqnarray}
with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$

Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
  Appendix \ref{sec:appendix_b} derives the characteristic functions for the summative random variables as:
\begin{align}
  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
\end{align}

Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
  it is natural that these variables also follow fixed distributions.
Moreover, they are independent to $\Sigma_v$.
This serves as conclusive evidence that
  these random variables follows consistent and fixed distributions,
  regardless of the underlying signal $\Sigma_v$.

@@

The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
Mathmatically, the sample covariance matrix is reduced to the sample variance
  and the determinant equates the scalar value.
On another hand, it is well known that for SAR data, variance equals intensity.
Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
This can be thought of 
  either as a cross-validation evidence for the proposed POLSAR models
  or alternatively as having SAR as the special case of POLSAR. 
%  with well known results for SAR intensity is presented.

The results so far for our models can be summarized as:
\begin{align}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
\end{align}

>>>>

\chapter{Scalar Models for the Multidimensional POLSAR data} %chapter 4
\label{chap:polsar}

This chapter derives several scalar statistical models for the
                determinant of the POLSAR covariance matrix and
                show that they are heteroskedastic in their original
                domain as well as homoskedastic in the log-transformed
                domain.
It
                also derives a heteroskedastic discrimination measures
                 as well as several homoskedastic measures of
                distance for the data.
Subsequently the statistical models for SAR are shown to be a special case of
                the proposed models for POLSAR
And finally these proposed models are validated against real-life practical data.
Mathematical derivations of the proposed models are presented in the Appendix. %***IVM: should say "Appendix A" or whatever it is?
%The last section of this chapter details the mathematical derivations of these proposed models,
%  which may only be helpful for mathematically inclined readers.

@@

In this section, the POLSAR scattering vector is denoted as $s$.
In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receive),
  the vector is two-dimensional ($d=2$) and is normally written as: 
%\begin{equation}
\begin{align*}  
s_{part}=\begin{bmatrix}
S_h\\ 
S_v
\end{bmatrix}
%\end{equation}
\end{align*}

In the case of full and monostatic POLSAR data,
  the vector is three-dimensional ($d=3$) and is presented as:
\begin{align*}
s_{full}=\begin{bmatrix}
S_{hh}\\
\sqrt{2}S_{hv}\\
S_{vv}
\end{bmatrix}
\end{align*}

Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
Assuming all the elements in $s$ are independent
  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
  then the probably density function (PDF) of $s$ can be written as:
\begin{equation}
  \label{eqn:POLSAR Target Vector: Complex Gaussian Distribution PDF}
  \caption{eqn:POLSAR Target Vector: Complex Gaussian Distribution PDF}
  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
\end{equation}
where $|M|$ denotes the determinant of the matrix $M$.

As the covariance matrix is only defined on multiple data points,
  the sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
These are formed as the mean Hermitian outer product of single-look scattering vectors
\begin{align*}
  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
\end{align*}
with $s_i$ denotes the single-look scattering vector,
  which equals $s_{part}$ in the case of partial POLSAR and
  $s_{full}$ in the case of full polarimetry,
and $L$ is the number of looks.

Complex Wishart distribution statistics, however, are normally written for the scaled covariance matrix
$Z=LC_v$, whose PDF is given as:
\begin{equation}
  \label{eqn:POLSAR Covariance Matrix: Complex Wishart Distribution PDF}
  \caption{eqn:POLSAR Covariance Matrix: Complex Wishart Distribution PDF}
  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
\end{equation}
with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
and $d$ is the dimensional number of the POLSAR covariance matrix.

Our approach differs by applying the homoskedastic log transformation
  on the determinant of the covariance matrix.
In \cite{Goodman_1963_AMS_178}, %Goodman
it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
\begin{equation}
\label{eqn:prod_chi_squared_rv}  
\caption{eqn:Determinant Ratio and the Product of Chi-Squared Distributions}
\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
\end{equation}

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\label{eqn:sum_log_chi_squared_rv}
\caption{eqn:Logarithm of Determinant Ratio and the Sum of Log-Chi-Squared Distributions}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

\section{Heteroskedastic POLSAR data and the Homoskedastic Log-Transformation}
\label{sec:polsar_heterosked_model_and_log_transform}

In this section the multiplicative nature of POLSAR data is illustrated.
Log-transformation is shown able to convert this into a more familiar additive model.
Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
  is proved to be the case for the original POLSAR data.
In log-transformed domain, the case for a homoskedastic model,
  whose variance is fixed and be independent of the underlying mean,
  is demonstrated.
To keep the section flowing, the mathematical derivation is only presented here in major sketches.
For more detailed derivation, please refer to Appendix \ref{chap:appendix_a}.

From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
we have:
\begin{equation}
  |C_v| \sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i)
  \label{eqn:determinant_distribution}
  \caption{eqn:POLSAR Covariance Matrix Determinant Distribution PDF}    
\end{equation}
\begin{equation}
  \ln|C_v| \sim \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
  \label{eqn:log_determinant_distribution}  
  \caption{eqn:POLSAR Covariance Matrix Log-Determinant Distribution PDF}    
\end{equation}

Over a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constants.
Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explanation that, 
  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
  the logarithmic transformation converts this into a more familiar additive noise.

Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
\begin{equation}
pdf(x;k) =
  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
\label{eqn:chi_squared_dist_pdf:chap4}
\caption{eqn:Chi-Squared Distribution PDF}
\end{equation}
Applying the variable change theorem, 
  its log-transformed variable follows the PDF of:
\begin{equation}
  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
\label{eqn:Log-Chi-Squared Distribution PDF}
\caption{eqn:Log-Chi-Squared Distribution PDF}
\end{equation}

Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
  can be written as:
  \begin{equation}
    CF_\chi(t) = (1-2it)^{−L}  
    \label{eqn:Log-Chi-Squared Distrbution: Characteristic Function}
    \caption{eqn:Log-Chi-Squared Distribution: Characteristic Function}
  \end{equation}
  \begin{equation}
    CF_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}
    \label{eqn:log_chi_squared_characteristic_function}
    \caption{eqn:Log-Chi-Squared Distribution: Characteristic Function}
  \end{equation}
Subsequently their means and variances can be computed from the given characteristic functions as:
  \begin{align*}
    avg \left[ \chi(2L) \right]&= 2L \\
var \left[ \chi(2L) \right]&= 4L \\
avg \left[ \Lambda(2L) \right] &= \psi^0(L) + \ln2 \\
var \left[ \Lambda(2L) \right] &= \psi^1(L)
  \end{align*}
  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma functions respectively.

@@

Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
%\begin{eqnarray}
%  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
%  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
%  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} 
%  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic} \caption{eqn:POLSAR Log Variance is independent from the underlying signal}
%\end{eqnarray}
\begin{equation}
avg \left[ |C_v| \right]  = \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)
\label{eqn:POLSAR Determinant is not biased}
\caption{eqn:POLSAR Determinant is not biased}
\end{equation}
\begin{equation}
  var \left[ |C_v| \right]  =   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}}
  \label{eqn:var_det_is_heteroskedastic}
  \caption{eqn:Variance of POLSAR Determinant is Heteroskedastic}
\end{equation}
\begin{equation}
  \label{eqn:avg_log_det}
  \caption{eqn:POLSAR Log-Determinant is biased}
  avg \left[ \ln |C_v| \right] = \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i)  
\end{equation}
\begin{equation}
  \label{eqn:var_log_det_is_homoskedastic}
  \caption{eqn:The Variance of POLSAR Log-Determinant is homoskedastic}
  var \left[ \ln |C_v| \right] =  \sum^{d-1}_{i=0} \psi^1(L-i)
\end{equation}

For a real captured image, while the parameters $d$ and $L$ do not change for the whole image,
  the underlying $\Sigma_v$ is expected to differ from one region to the next.
Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
In such a context, Eqn. \ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$, hence exhibiting its homoskedastic nature.

@@

This section introduces the consistent sense of distance from a few different perspectives.
First assuming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
the following random variables,
  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observables according to their definitions:

\begin{equation}
 \label{eqn:determinant_ratio_observables}
 \caption{eqn:POLSAR Determinant-Ratio Observable}
 \mathbb{R} = \frac{|C_v|}{|\Sigma_v|}
\end{equation}
\begin{equation}
 \label{eqn:log_distance_observables}
 \caption{eqn:POLSAR Log-Distance Observable}
 \mathbb{L} = \ln|C_v| - \ln|\Sigma_v|  
\end{equation}

From another perspective where the POLSAR is known as having come from an homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
\begin{eqnarray}
\end{eqnarray}
\begin{equation}
 \label{eqn:dispersion_observable}
 \caption{eqn:POLSAR Dispersion Observable}
 \mathbb{D} = \ln{|C_v|} - avg(\ln{|C_v|})  
\end{equation}
\begin{equation}
  \label{eqn:contrast_observable}
  \caption{eqn:POLSAR Contrast Observable}
  \mathbb{C} = \ln(|C_{v1}|) - \ln(|C_{v2}|)
\end{equation}

Applying Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det}, Eqns \ref{eqn:determinant_ratio_observables} to \ref{eqn:contrast_observable} becomes:
\begin{equation}
 \label{eqn:determinant_ratio_distribution}
 \caption{eqn:POLSAR Determinant Ratio Distribution PDF}
 \mathbb{R} \sim \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) 
\end{equation}
\begin{equation}
\mathbb{L} \sim  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
\label{eqn:log_determinant_distance_distribution}  
 \caption{eqn:POLSAR Log-Distance Distribution PDF}
\end{equation}
\begin{equation}
 \mathbb{D} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k_D
\label{eqn:dispersion_distribution}  
 \caption{eqn:POLSAR Dispersion Distribution PDF}
\end{equation}
\begin{equation}
 \mathbb{C} \sim \sum^{d-1}_{i=0} \Delta(2L-2i)
\label{eqn:contrast_distribution}  
 \caption{eqn:POLSAR Contrast Distribution PDF}
\end{equation}
with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
and $k_D=\sum^{d-1}_{i=0} \psi^0(L-i)$

Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
  %Section \ref{sec:appendix_b} derives
  the characteristic functions for the summative random variables can be derived as:
\begin{align*}
  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
\end{align*}

Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
  it is natural that these variables also follow fixed distributions.
Moreover, they are independent of $\Sigma_v$.
This serves as conclusive evidence that
  these random variables follow consistent and fixed distributions,
  regardless of the underlying signal $\Sigma_v$.

@@

The prevous section has validated the use of our models for 3-dimensional (d = 3)
full polarimetric and 2-dimensional (d = 2) partial polarimetric SAR cases. In this
section, the focus is on the limit case where the dimensional number is reduced to 1,
i.e. d = 1. Physically this means that when the multi-dimensional POLSAR dataset is collapsed
into the one dimension, it becomes conventional  SAR data. Mathematically, the sample covariance
matrix is reduced to the sample variance and the determinant equates the scalar value.
Since  it is well known that, for SAR data, variance equals intensity,
the special case of the d = 1 result should be consistent
with previous results for SAR intensity data. This can be thought of either as a cross-validation evidence for the proposed POLSAR models, or alternatively as having SAR
as the special case of POLSAR.

The results so far for our models can be summarized as:
\begin{align*}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) %\label{eqn:polsar_dispersion_mse} 
\end{align*}
